Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-17 main.tex
sequentialisation

We define a congruence relation $\fequ$ on formulas by the following equations:
\begin{equation*}
  \begin{array}{cc}
    A \vlan B \fequ B \vlan A & A \vlor B \fequ B \vlor A \\
    (A \vlan B) \vlan C \fequ A \vlan (B \vlan C) &
    (A \vlor B) \vlor C \fequ A \vlor (B \vlor C) \\
    \forall x . \forall y . A \fequ \forall y . \forall x . A &
    \exists x . \exists y . A \fequ \exists y . \exists x . A \\
    \forall x . (A \vlor B) \fequ (\forall x . A) \vlor B &
    \exists x . (A \vlan B) \fequ (\exists x . A) \vlan B
  \end{array}
\end{equation*}
where $x \notin fv(B)$ in the last two equations.
Two formulas $A$ and $B$ are \bfit{equivalent} if $A \fequ B$. The following
theorem shows that the set of fographs can been seen as the quotient
$\FORM / \fequ$.
\begin{thm}
  Let $A,B$ be rectified formulas. Then
  $$
  A\fequ B \iff \graphof A =\graphof B
  $$
\end{thm}

@@

Now we consider the inductive cases:
\begin{itemize}
  \item $\Gamma = \Delta, A \vlor B$:
  \item $\Gamma = \Delta \forall x.A$:
\end{itemize}

>>>>

We define a congruence relation $\fequ$ on formulas by the following equations:
\begin{equation}
  \label{eq:fequ}
  \begin{array}{cc}
    A \vlan B \fequ B \vlan A & A \vlor B \fequ B \vlor A \\
    (A \vlan B) \vlan C \fequ A \vlan (B \vlan C) &
    (A \vlor B) \vlor C \fequ A \vlor (B \vlor C) \\
    \forall x . \forall y . A \fequ \forall y . \forall x . A &
    \exists x . \exists y . A \fequ \exists y . \exists x . A \\
    \forall x . (A \vlor B) \fequ (\forall x . A) \vlor B &
    \exists x . (A \vlan B) \fequ (\exists x . A) \vlan B
  \end{array}
\end{equation}
where $x \notin fv(B)$ in the last two equations.
Two formulas $A$ and $B$ are \bfit{equivalent} if $A \fequ B$. The following
theorem shows that the set of fographs can been seen as the quotient
$\FORM / \fequ$.
\begin{thm}
  Let $A,B$ be rectified formulas. Then
  $$
  A\fequ B \iff \graphof A =\graphof B
  $$
\end{thm}

@@

Now we consider the inductive cases:
\begin{itemize}
  \item $\Gamma = \Delta, A \vlor B$:
    Let $\Gamma' = \Delta, A, B$. Define $\lambda'$ on $\Gamma'$ using the same
    links as $\lambda$ by identifying the leaves of $\formtree{\Gamma'}$ with those
    of $\formtree{\Gamma}$. We now check that $\lambda'$ is a unification net:
    \begin{itemize}
      \item The most general dualizer of $\lambda$ is also the most general
dualizer of $\lambda'$ as they correspond to the same unification problem.
Hence, the unification structure $\unifstr{\lambda'}$ is equal to the
restriction of $\unifstr{\lambda}$ to the nodes of $\formtree{\Gamma'}$.
      \item Every switching graph of $\lambda'$ is acyclic: if there were some
switching graph of $\unifstr{\lambda'}$ containing a cycle, it would induce a switching
graph of $\unifstr{\lambda}$ containing also a cycle, by adding an edge from the root of
$\formtree{A}$ to the $\vlor$ node in question.
    \end{itemize}
  \item $\Gamma = \Delta, \forall x.A$:
    Let $\Gamma' = \Delta, A$. Define $\lambda'$ on $\Gamma'$ using the same
links as $\lambda$. We now check that $\lambda'$ is a unification net:
  \begin{itemize}
    \item The most general dualizer of $\lambda$ is also the most general
dualizer of $\lambda'$ as they correspond to the same unification problem.
    \item Every switching graph of $\unifstr{\lambda'}$ is acyclic: if there
were some switching graph of $\unifstr{\lambda'}$ containing a cycle, it would
induce a switching graph of $\unifstr{\lambda}$ contaiting also a cycle, by
adding an edge from the root of $\formtree{A}$ to the $\forall$ node in
question.
  \end{itemize}
  \item $\formtree{\Gamma}$ has a root $\exists x$ with no outgoing dependency
edge:
\end{itemize}
